Fast and exact visibility on digitized shapes and application to feature-aware normal estimation

### 2025-03-21 DGMM2025/paper.tex
Small fix

%
\begin{document}
%
\title{Fast and exact visibility on digitized shapes and application to feature-aware normal estimation and pattern detection}
%
\titlerunning{Fast and exact visibility on digitized shapes}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Romain Negro\inst{1}\orcidID{0000-XXXX-YYYY-ZZZZ} \and
  Jacques-Olivier Lachaud\inst{1}\orcidID{0000-0003-4236-2133}}
%
\authorrunning{R. Negro and J.-O. Lachaud}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Universit\'e Savoie Mont Blanc, CNRS, LAMA, F-73000 Chambéry, France\\
  \email{\{romain.negro|jacques-olivier.lachaud\}@univ-smb.fr}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
  Our abstract
\keywords{Visibility \and Geometric inference \and Digital normal estimation \and Digital geometry} 
\end{abstract}

@@

>>>>

%
\begin{document}
%
\title{Fast and exact visibility on digitized shapes and application to feature-aware normal estimation}
%
\titlerunning{Fast and exact visibility on digitized shapes}
% If the paper title is too long for the running head, you can set
% an abbreviated paper title here
%
\author{Romain Negro\inst{1}\orcidID{0000-XXXX-YYYY-ZZZZ} \and
  Jacques-Olivier Lachaud\inst{1}\orcidID{0000-0003-4236-2133}}
%
\authorrunning{R. Negro and J.-O. Lachaud}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{Universit\'e Savoie Mont Blanc, CNRS, LAMA, F-73000 Chambéry, France\\
  \email{\{romain.negro|jacques-olivier.lachaud\}@univ-smb.fr}}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
  Our abstract
\keywords{Visibility \and Geometric inference \and Digital normal estimation \and Digital geometry} 
\end{abstract}

@@

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Visibility through tangency of chords}

Introduce full convexity and tangency. \cite{lachaud:2021-dgmm,Lachaud:2022-jmiv}.

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Fast computation using integer intervals intersections}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Feature-aware normal estimation on digital surfaces}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\section{Conclusion}

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\begin{credits}
  \subsubsection{\ackname}
  This work is partially supported by the French National Research Agency
  within the StableProxies project (ANR-22-CE46-0006).
%% \subsubsection{\discintname}
%% It is now necessary to declare any competing interests or to specifically
%% state that the authors have no competing interests. Please place the
%% statement with a bold run-in heading in small font size beneath the
%% (optional) acknowledgments\footnote{If EquinOCS, our proceedings submission
%% system, is used, then the disclaimer can be provided directly in the system.},
%% for example: The authors have no competing interests to declare that are
%% relevant to the content of this article. Or: Author A has received research
%% grants from Company W. Author B has received a speaker honorarium from
%% Company X and owns stock in Company Y. Author C is a member of committee Z.
\end{credits}
%
% ---- Bibliography ----
%
% BibTeX users should specify bibliography style 'splncs04'.
% References will then be sorted and formatted in the correct style.
%
\bibliographystyle{splncs04}
\bibliography{biblio}
